*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-22 Code/Manuscript_O2.Rmd
Edits to protein materials and methods

*Prochlorococcus marinus*, a genus of the phylum Cyanobacteria, is the smallest known photosynthetic prokaryote, with cell diameters ranging from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992]. Despite small cell size, *P. marinus* contribute 13 to 48% of net primary production in oligotrophic oceans, corresponding to about 30% of  global oxygen production [@partenskyProchlorococcusMarinePhotosynthetic1999].  *P. marinus* growth is currently constrained to between latitudes of 40°N to 40°S in open ocean waters, from surface to 300 m  depth, thus spanning 3 orders of magnitudes of light (Partensky et al., 1999) (Chisholm et al., 1992)  [@partenskyProchlorococcusMarinePhotosynthetic1999].

@@

XXXXMIREILLE Check strain descriptions for accuracyXXXX
Low-Light clades thrive in deeper ocean waters, extending beyond 200 m in depth [@partenskyProchlorococcusMarinePhotosynthetic1999], where only ~1% of the surface irradiance penetrates, primarily in the blue (450 nm) to green (520 nm) spectral ranges [@holtropVibrationalModesWater2021]. Clade LLIV, including cultured strain MIT9313, falls near the base of the *Prochlorococcus* radiation, and is characterized by preference for low light, at depths from 120 m and 200 m (Partensky et al., 1999). LLIV members are, as yet, the only cultured strains found in Oxygen Minimum Zones (OMZ).  Some as yet uncultured *P. marinus* strains in clades LLV and LLVI thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021; @@lavinNovelLineagesProchlorococcus2010; @goerickeNovelNicheProchlorococcus2000; @garcia-robledoCrypticOxygenCycling2017a] (Johnson et al., 1999). *P. marinus* LL ecotypes may indeed dominate the phytoplankton within OMZ
[@lavinNovelLineagesProchlorococcus2010;
@ulloaCyanobacteriumProchlorococcusHas2021; @partenskyProchlorococcusAdvantagesLimits2010].

@@

All samples and appropriate standards were prepared as described in [@brownFluxCapacitiesAcclimation2008]. Standards were obtained from Agrisera (Vännäs, Sweden; FtsH AS11 1789S; PsbA AS01 016S; PetC AS08 330S; PsaC AS04 042S; RbcL AS01 017S).  Between 0.1 to 4.0 µg of total protein was loaded onto 15 well Invitrogen Bolt 4-12% acrylamide Bis-Tris gels (ThermoFisher Scientific, Waltham, MA, USA). All gels were run for 25 minutes at 200V using Invitrogen Bolt Mini Gel tanks and Invitrogen Bolt MES SDS running buffer (ThermoFisher Scientific, Waltham, MA, USA) and transferred for 60 minutes at 20V onto a PVDF membrane (Bio-Rad, Hercules, CA, USA; SKU 1620177). Blots were blocked overnight in 2% ECL blocking solution as described by @brownFluxCapacitiesAcclimation2008. The following morning, each blot was incubated in their appropriate antibody obtained from Agrisera (Vännäs, Sweden; FtsH  1:5,000 dilution, AS11 1789; PsbA  1:10000 dilution, AS05 084; PetC 1:XXXXX dilution, AS08 330; PsaC 1:XXXXXX dilution, AS10 939; RbcL 1:10000 dilution, AS03 037) and a 1:15000 dilution of the secondary antibody, goat anti-rabbit HRP conjugated (Bio-Rad, Hercules, CA, USA; SKU 1706515, lot 64230791).  Blots were incubated in Amersham ECL Select chemiluminescent substrate (Danaher, Washington, DC, USA) and imaged in a Bio-Rad VersaDoc imager (Bio-Rad, Hercules, CA, USA). Images were quantitated using the ImageJ2 software (version 1.53c).

>>>>

*Prochlorococcus marinus*, a genus of the phylum Cyanobacteria, is the smallest known photosynthetic prokaryote, with cell diameters ranging from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992]. Despite small cell size, *P. marinus* contribute 13 to 48% of net primary production in oligotrophic oceans, corresponding to about 30% of  global oxygen production [@partenskyProchlorococcusMarinePhotosynthetic1999].  *P. marinus* growth is currently constrained to between latitudes of 40°N to 40°S in open ocean waters, from surface to 300 m  depth, thus spanning 3 orders of magnitudes of light [@partenskyProchlorococcusMarinePhotosynthetic1999; @chisholmProchlorococcusMarinusNov1992 ].

@@

XXXXMIREILLE Check strain descriptions for accuracyXXXX
Low-Light clades thrive in deeper ocean waters, extending beyond 200 m in depth [@partenskyProchlorococcusMarinePhotosynthetic1999], where only ~1% of the surface irradiance penetrates, primarily in the blue (450 nm) to green (520 nm) spectral ranges [@holtropVibrationalModesWater2021]. Clade LLIV, including cultured strain MIT9313, falls near the base of the *Prochlorococcus* radiation, and is characterized by preference for low light, at depths from 120 m and 200 m (Partensky et al., 1999). LLIV members are, as yet, the only cultured strains found in Oxygen Minimum Zones (OMZ).  Some as yet uncultured *P. marinus* strains in clades LLV and LLVI thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021; @lavinNovelLineagesProchlorococcus2010; @goerickeNovelNicheProchlorococcus2000; @robledoCrypticOxygenCycling2017] (Johnson et al., 1999). *P. marinus* LL ecotypes may indeed dominate the phytoplankton within OMZ
[@lavinNovelLineagesProchlorococcus2010;
@ulloaCyanobacteriumProchlorococcusHas2021; @partenskyProchlorococcusAdvantagesLimits2010].

@@

All samples and appropriate standards were prepared as described in [@brownFluxCapacitiesAcclimation2008]. Standards were obtained from Agrisera (Vännäs, Sweden; FtsH AS11 1789S; PsbA AS01 016S; PetC AS08 330S; PsaC AS04 042S; RbcL AS01 017S).  Between 0.1 to 4.0 µg of total protein was loaded onto 15 well Invitrogen Bolt 4-12% acrylamide Bis-Tris gels (ThermoFisher Scientific, Waltham, MA, USA). All gels were run for 25 minutes at 200V using Invitrogen Bolt Mini Gel tanks and Invitrogen Bolt MES SDS running buffer (ThermoFisher Scientific, Waltham, MA, USA) and transferred for 60 minutes at 20V onto a PVDF membrane (Bio-Rad, Hercules, CA, USA; SKU 1620177). Blots were blocked overnight in 2% ECL blocking solution as described by @brownFluxCapacitiesAcclimation2008. The following morning, each blot was incubated in their appropriate antibody obtained from Agrisera (Vännäs, Sweden; FtsH  1:5000 dilution, AS11 1789; PsbA  1:10000 dilution, AS05 084; PetC 1:10000 dilution, AS08 330; PsaC 1:5000 dilution, AS10 939; RbcL 1:10000 dilution, AS03 037) and a 1:15000 dilution of the secondary antibody, goat anti-rabbit HRP conjugated (Bio-Rad, Hercules, CA, USA; SKU 1706515, lot 64230791).  Blots were incubated in Amersham ECL Select chemiluminescent substrate (Danaher, Washington, DC, USA) and imaged in a Bio-Rad VersaDoc imager (Bio-Rad, Hercules, CA, USA). Images were quantitated using the ImageJ2 software (version 1.53c).
